\documentclass[11pt]{article}

\usepackage[hmargin=1in,vmargin=0.8in]{geometry}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}


% For better handling of unicode (Latin characters, anyway)
\IfFileExists{lmodern.sty}{\usepackage{lmodern}}{}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=red,
    linktoc=all
}

\RequirePackage{filecontents}
\begin{filecontents*}{bibliografie.bib}

@misc{culling,
  author = "Wikipédia",
  title = "Détermination des surfaces cachées",
  howpublished = "\newline\url{https://fr.wikipedia.org/wiki/Détermination_des_surfaces_cachées}",
  note = "\newline Date d'accès: 22 Janvier 2017"
}

\end{filecontents*}

\title{Graphic User Interface (GUI) : technical implementation}
\author{Romain PEREIRA}
\date{29th October 2017}

\renewcommand*\contentsname{Summary}

\begin{document}
	\maketitle
	This draft on the vast topic of graphical interfaces is only meant to document my VoxelEngine. I do not pretend this to be a formal document! Still, I will try to stick to a standard scientific publication format, to make readable and interesting.
	\newline
	\newline
	Thank you for your attention, have a nice reading, and feel free to report me any mistakes I could have written.
	\tableofcontents
	\newpage

	\section*{Abstract}
	
	• `states the question investigated and the principal objectives of the investigation,

	• When developping my game engine, I faced the problem of implementing graphic user interfaces (GUI)
	I wanted to implement a robust but still flexible GUI system, so that I (or anyone else), can re-use it and customize it easily on any other OpenGL projects.
	
	• So far, I have implemented a this GUI library: it handles input events and the entire rendering pipeline, in modern OpenGL (4.0)

	• ` summarizes your results, and  states your major conclusions.
	
	\newpage

	\section{Introduction}
	In this document, I will explain how I've implemented the graphic user interface system in my VoxelEngine.
	There is not many prerequisites to understand this paper, only a basic knowledge of computer programming and modern graphic rendering should be enough.
	\newpage

	\section{Materials and methods}
		\subsection{Components (attributes, rendering...)}
			\subsubsection{Abstract GUI component definition}
			\subsubsection{Colored rectangle}
			\subsubsection{Texture}
			\subsubsection{Text (or Label)}
			\subsubsection{Button}
			\subsubsection{More complex components...}

		\subsection{Inputs}
			\subsubsection{Component states}
			\subsubsection{Listeners and Events}
			\subsubsection{Custom controllers}

		\subsection{GUI manager}
			\subsubsection{Controler}
			\subsubsection{Renderer}

	\newpage
	
	\section{General conclusion}
	\newpage
	
	\nocite{*}
	\bibliographystyle{amsplain}
	\bibliography{bibliografie}


\end{document}